I am extremely grateful to Berthier for his valuable advice
and encouragement during the course of my master's. His guidance was important not only
in the intellectual pursuit that led to this dissertation, but in a general
sense. His insightful observations about questions that go far beyond Computer Science
are an enduring source of inspiration. 

I would like to extend my gratitude to Alberto
Ueda, for his extraordinarily detailed review that contributed quite a lot to the quality 
of this work. I also thank him, Filipe, Gabriel, Fabricio, Alef, Amir, and all the lab
fellows from LATIN and PENSI for their friendship and support during the whole process.
My life has changed forever for the better by getting to know this awesome
group of people.

Many thanks to Nivio for his support in the laboratory and for his relentless enthusiasm 
in promoting science and technology that is a great source of inspiration. Also, many
thanks to Adriano for introducing me to the field of Machine Learning and for his very 
helpful research advices. I also extend my sincere thanks to all professors in the 
department that inspired me during lessons and day to day conversations.

I would like to gratefully acknowledge the assistance provided by Sonia Borges during
my many visits to the postgraduate office. Also, I would like to thank our
representatives, Evellyn and Evelin, for their determined struggle to improve the 
well-being of the other students, many times at the expense of their own welfare.

I am extremely grateful to my mother, my father and my brother for their support 
in every aspect of life. My mother taught me to value education and 
to seek knowledge everywhere. My father taught me to work hard 
to achieve my goals and make a difference. My brother taught me to think
big and to think differently. But, above all else, they made me who I am today.

Lastly, I thank all the friends and family that were not directly involved in the 
process of writing this dissertation but were always present in my life.
